### 2015-03-02 ThesisJo/introduction.tex
la2pdf commit - 2015:03:02	13:41:35	(Mon 2.Mar)
la2pdf commit - 2015:03:02	14:36:38	(Mon 2.Mar)

@@

where $\nabla^2$ is the Laplacian operator

>>>>

When a rock is thrown into a pound of water it abruptly displaces water at the location of impact. This is an unstable state where various physical forces compete for order. Gravity wants the water back where it wants, but due to inertia the mass will resist any change in its motion. The wrestling of these forces result in a spherical wave propagating from the displacement centre.

@@

where $\nabla^2$ is the Laplacian operator. The wave equation constrains the magnitude of the wavenumber,
%
\begin{align*}
\vec k = \frac{\omega}{c} = \frac{2\pi}{\lambda},
\end{align*}
%
so only the direction of $\k$ varies.
